QPLIB: A Library of Quadratic Programming Instances

### 2018-02-12 QPLIB-2.2.tex
update todos

This description is deliberately coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flows \cite{FrFG16,FrGaSc14,FrGaSt16a,FGGP11,tadayon-smith:2013} or knapsack-type linear constraints \cite{FrFG16,FrGo13b,FGGP11}, and semi-continuous variables \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe06a,FrGe07a,FrGe09a,FGGP11},
%\todo{SV: do we really need 7 Frangioni et.al citations for semi-continuous variables?}
or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe09a,FGGP11}.
%\todo{SV: 5 Frangioni et.al citations for SOC?}. 

>>>>

This description is deliberately coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flows \cite{FrFG16,FrGaSc14,FrGaSt16a,FGGP11,tadayon-smith:2013} or knapsack-type linear constraints \cite{FrFG16,FrGo13b,FGGP11}, and semi-continuous variables \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe06a,FrGe07a,FrGe09a,FGGP11}
\todo{SV: reduce to 1-3 citations here},
or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe09a,FGGP11}
\todo{SV: reduce to 1-3 citations here}.

### 2018-02-12 QPLIB-3.tex
update todos

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others. \textcolor{red}{In addition, we mention
that other generic libraries exist, e.g., 
Conic library CBLIB (\url{http://cblib.zib.de}) and 
MIPLIB~2010 (\url{http://miplib.zib.de/}), to mention just a few.}
%\todo{AG: maybe cite CBLIB paper \cite{Friberg2016} SV: then we would have to add citations for all mentioned libraries (where available)}

@@

The QPLIB instances are publicly accessible at the website \url{http://qplib.zib.de}, which was created by extending
scripts and tools initially developed for MINLPLib\,2~\cite{Vigerske2014}.
%
We provide all instances in GAMS (\texttt{.gms}), AMPL (\texttt{.mod}), CPLEX (\texttt{.lp})
\cite{,cplex}, and  QPLIB (\texttt{.qplib}) formats. The latter is a new format
specifically for QP instances. In comparison to more \emph{high level}
formats such as \texttt{.gms} and \texttt{.lp}, the new
format offers three main advantages: it is easier to read by a stand-alone
parser, 
%(provided)\todo{SV: what is meant by ``(provided)''?}, 
it typically produces smaller files, and it permits the
inclusion of two-sided inequalities without needless repetition of data.
%the order of variables and constraints is fixed.
See Appendix~\ref{sec:format} for more details.

>>>>

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others. \textcolor{red}{In addition, we mention
that other generic libraries exist, e.g., 
Conic library CBLIB (\url{http://cblib.zib.de}) and 
MIPLIB~2010 (\url{http://miplib.zib.de/}), to mention just a few.}

@@

The QPLIB instances are publicly accessible at the website \url{http://qplib.zib.de}, which was created by extending
scripts and tools initially developed for MINLPLib\,2~\cite{Vigerske2014}.
%
We provide all instances in GAMS (\texttt{.gms}), AMPL (\texttt{.mod}), CPLEX (\texttt{.lp})
\cite{,cplex}, and  QPLIB (\texttt{.qplib}) formats. The latter is a new format
specifically for QP instances. In comparison to more \emph{high level}
formats such as \texttt{.gms} and \texttt{.lp}, the new
format offers three main advantages: it is easier to read by a stand-alone
parser,
it typically produces smaller files, and it permits the
inclusion of two-sided inequalities without needless repetition of data.
%the order of variables and constraints is fixed.
See Appendix~\ref{sec:format} for more details.
